### 2014-11-11 locks.tex
Update paper with new table.

These experiments indicate that handling coordination has a small cost that is
greatly offset by improved performance. In general, coordination reduces the
amount of locking required in the overall program because the number of facts
needed to be derived is reduced. Even in cases where the amount of locking
increases, it is still better to use coordination due to less synchronization
between threads.

>>>>

We also measured the number of queue instructions required to compute programs.
While the regular queue operations have constant complexity, priority queue
operations are usually logarithmic and require more computation. We counted the
number of instructions required for queue operations during program execution.
Each normal queue operation costs 1 instruction, while priority queue costs as
many \emph{percolate-up}/\emph{percolate-down} instructions are required to maintain the heap property.

Table~\ref{queue_instructions} presents the total queue instructions for several
programs. All the coordinated programs require far more queue instructions than
the regular version. For instance, the coordinated SSSP program requires 3 to 4
times more instructions to perform queue operations. Interestingly, the buffered
version requires even more instructions although it performs less overall
coordination. It is likely that this is due to increased fact computation and
subsequent queue manipulation. We argue that the 5\% performance improvement in the
buffered version is due mostly to reduced locking.

For the HT program, the coordinated version requires twice more queue
instructions than the regular version. As expected, the local-only version
requires less queue operations because the number of derived facts is reduced.

\begin{topfig}
\footnotesize\begin{tabular}{ | l || c | c | c | c | c |}
\hline
\multirow{2}{*}{\textbf{Program}} & \multicolumn{5}{c |}{\textbf{Queue
   Instructions}} \\ \cline{2-6}
& 1 & 2 & 4 & 8 & 16 \\ \hline
\hline
SSSP - Regular & 298K & 305K & 309K & 286K & 325K \\ \hline
SSSP - Coordinated & 961K & 919K & 903K & 900K & 922K \\ \hline
SSSP - Buffered & 939K & 961K & 999K & 926K & 1M \\ \hline
\hline
HT - Buffered & 38M & 49M & 50M & 52M & 54M \\ \hline
HT - Coordinated & 57M & 63M & 95M & 89M & 82M \\ \hline
HT - Local-Only & 57M & 63M & 91M & 80M & 74M \\ \hline
\hline
LBP - Regular & 23M & 26M & 24M & 17M & 12M \\ \hline
SBP - Coordinated & 95M & 93M & 88M & 81M & 75M \\ \hline
\hline
MiniMax - Regular & 24M & 26M & 27M & 26M & 27M \\ \hline
MiniMax - Coordinated & 51M & 51M & 52M & 51M & 52M \\ \hline
\end{tabular}
\scap{queue_instructions}{Number of queue \scare{instructions} per program. An
   operation to a regular queue counts as 1 instruction, while an operation to
   a priority queue costs the number of
   \emph{percolate-up}/\emph{percolate-down} steps performed.}
\end{topfig}

These experiments indicate that handling coordination has a small cost in terms
of synchronization but some cost in terms of queue operations with
up to 5 times more queue instructions when using priority queues.
Since coordination reduces the number of facts derived due to better scheduling
decisions, the costs of manipulating priority queues become irrelevant.
